Modelling BCG vaccination in the UK

### 2019-12-16 rmds/07-direct-effect-bcg-change.Rmd
checked and updated direct effects equations

\begin{equation}
C^i_P = C_{UE}(1 - I^i),\ \text{Where}\ i = e,\ l,\ u.
\end{equation}

where $C_{UE}$ is the number of cases observed assuming that the cohort was not exposed to targeted high-risk neonatal vaccination. As from 2005 onwards this cohort were in fact exposed to this vaccination scheme an additional step was required. This first required calculating the number of cases that would be expected if the cohort had not been exposed to the scheme,

\begin{equation}
C_{UE} = \frac{C_0}{I^i}
\end{equation}

and then combining this with the previous equation so that $C^i_P$ can be estimated with observed data ($C_0$).

>>>>

\begin{equation}
C^i_P = C_{NE}(1 - I^i),\ \text{Where}\ i = e,\ l,\ u.
\end{equation}

Where $C_{NE}$ is the number of cases observed assuming that the cohort was not exposed to targeted high-risk neonatal vaccination. As from 2005 onwards this cohort were in fact exposed to this vaccination scheme an additional step was required. This first required calculating the number of cases that would be expected if the cohort had not been exposed to the scheme,

\begin{equation}
C_{NE} = \frac{C_0}{I^i}
\end{equation}

Then combining this with the previous equation so that $C^i_P$ can be estimated using observed data ($C_0$),
